Algomusicology, ????, Profit

### 2016-07-23 paper.tex
Incorporate detailed feedback from reviewer 1.

Less glibly, is algomusicology doomed to be a mere observer and explainer of musical practice, or might it become an
active participant in the conversation? Computer science is able to influence the software industry, though that might take longer
than we'd like.~\footnote{Alonzo Church developed the lambda calculus in the 1930s. Java gained lambda expressions in 2015.}
Can algomusicology influence music?~\footnote{This paper appears to be the first reference to algomusicology. I use the term,
which is a portmanteau of algorave and musicology, to describe the use of information theory and programming for musical analysis.}

@@

\section{Air on the {\textbackslash}G String\cite{Air on the G String}}
Very great quantities of data can exhibit very little complexity. Consider the following Clojure expression, which
evaluates to a sequence of $10^{15}$ uppercase G characters:

@@

The Kleene star is the set of all possible strings that can be built from a set of elements. Here is a function that takes a set
of elements and enumerates the Kleene star a lazy sequence. It works by taking the strings generated thus far, appending each
element to each string and then repeating the process. This results in an infinite lazy sequence of strings of ever increasing
length, starting from the empty string.

@@

For the Gayte-Williams-Thicke constant. I wrote a version of `Blurred Lines' with three parts and used a three part encoding.
The piece presented is actually lexicon for music of up to three parts using equal temperament and notes with simple
fractional durations, not all possible sound art pieces.

@@

\bibitem{Overtone} Aaron, Sam and Rose, Jeff: Overtone, \url{https://overtone.github.io}.
\bibitem{Anti EP} Autechre (Rob Brown and Sean Booth): Anti EP, \textit{Warp Records}, 1994.
\bibitem{The Library of Babel} Borges, Jorge Luis: `The Library of Babel' in The Garden of Forking Paths, \textit{Editorial Sur}, 1941.
\bibitem{Gnomes} Brady, Pam, Parker, Trey and Stone, Matt: Gnomes, Episode 17, Season 2 of \textit{South Park}, 1998.
\bibitem{The construction of decimals normal in the scale of ten} Champernowne, David: The construction of decimals normal in the scale of ten, \textit{Journal of the London Mathematical Society}, volume 8, 1933.
\bibitem{Leipzig} Ford, Chris: Leipzig, \url{https://github.com/ctford/leipzig}.
\bibitem{Joseph Gallivan on pop} Gallivan, Joseph: Joseph Gallivan on pop, \textit{The Independent}, July 18, 1994.
\bibitem{Got to Give It Up} Gaye, Marvin: Got to Give It Up, \textit{Tamla}, 1977.
\bibitem{Clojure} Hickey, Rich: Clojure, \url{http://clojure.org/}
\bibitem{On Tables of Random Numbers}  Kolmogorov, Andrey: On Tables of Random Numbers, \textit{Sankhyā Series A}, volume 25, 1963.
\bibitem{Midje} Marick, Brian: Midje, \url{https://github.com/marick/Midje}.
\bibitem{Analysis by Compression} Meredith, David: Analysis by Compression, \textit{The Music Encoding Conference}, 2013.
\bibitem{USA Today} Oldenburg, Ann: `Blurred Lines' jury finds for Marvin Gaye, \textit{USA Today}, March 11, 2015.
\bibitem{Contact} Sagan, Carl: Contact, \textit{Simon and Schuster}, 1985.
\bibitem{Propositions as Types} Wadler, Philip: Propositions as Types, \textit{Communications of the ACM}, volume 58, issue 12, 2015.
\bibitem{Air on the G String} Wilhelmj, August arranging Bach, Johann Sebastian: Air on the G String, late 19th century.
\bibitem{Blurred Lines} Williams, Pharrel and Thicke, Robin: Blurred Lines, \textit{Star Trak Recordings}, 2013.

>>>>

Less glibly, is algomusicology doomed to be a mere observer and explainer of musical practice, or might it become an
active participant in the conversation? Computer science is able to influence the software industry, though that might take longer
than we'd like.~\footnote{Alonzo Church developed the lambda calculus in the 1930s. Java gained lambda expressions in 2015.}
Can algomusicology influence music?~\footnote{This paper appears to be the first reference to algomusicology. I use the term,
which is a portmanteau of algorithm and musicology similar to algorave, to describe the use of information theory and programming for musical analysis.}

@@

\section{Air on the {\textbackslash}G String}
Very great quantities of data can exhibit very little complexity. Consider the following Clojure expression, which
evaluates to a sequence of $10^{15}$ uppercase G characters:

@@

The Kleene star is the set of all possible strings that can be built from a set of elements. Here is a function that takes a set
of elements and enumerates the Kleene star as a lazy sequence. It works by taking the strings generated thus far, appending each
element to each string and then repeating the process. This results in an infinite lazy sequence of strings of ever increasing
length, starting from the empty string.

@@

For the Gayte-Williams-Thicke constant, I wrote a version of `Blurred Lines' with three parts and used a three part encoding.
The piece presented is actually lexicon for music of up to three parts using equal temperament and notes with simple
fractional durations, not all possible sound art pieces.

@@

\bibitem{Overtone} Aaron, Sam and Rose, Jeff: Overtone, \url{https://overtone.github.io}.
\bibitem{Anti EP} Autechre (Rob Brown and Sean Booth): Anti EP, \textit{Warp Records}, 1994.
\bibitem{The Library of Babel} Borges, Jorge Luis: `The Library of Babel' in The Garden of Forking Paths, \textit{Editorial Sur}, 1941.
\bibitem{Gnomes} Brady, Pam, Parker, Trey and Stone, Matt: Gnomes, Episode 17, Season 2 of \textit{South Park}, 1998.
\bibitem{The construction of decimals normal in the scale of ten} Champernowne, David: The construction of decimals normal in the scale of ten, \textit{Journal of the London Mathematical Society}, volume 8, 1933.
\bibitem{Leipzig} Ford, Chris: Leipzig, \url{https://github.com/ctford/leipzig}.
\bibitem{Joseph Gallivan on pop} Gallivan, Joseph: Joseph Gallivan on pop, \textit{The Independent}, July 18, 1994.
\bibitem{Got to Give It Up} Gaye, Marvin: Got to Give It Up, \textit{Tamla}, 1977.
\bibitem{Clojure} Hickey, Rich: Clojure, \url{http://clojure.org/}
\bibitem{On Tables of Random Numbers}  Kolmogorov, Andrey: On Tables of Random Numbers, \textit{Sankhyā Series A}, volume 25, 1963.
\bibitem{Midje} Marick, Brian: Midje, \url{https://github.com/marick/Midje}.
\bibitem{Analysis by Compression} Meredith, David: Analysis by Compression, \textit{The Music Encoding Conference}, 2013.
\bibitem{USA Today} Oldenburg, Ann: `Blurred Lines' jury finds for Marvin Gaye, \textit{USA Today}, March 11, 2015.
\bibitem{Contact} Sagan, Carl: Contact, \textit{Simon and Schuster}, 1985.
\bibitem{Propositions as Types} Wadler, Philip: Propositions as Types, \textit{Communications of the ACM}, volume 58, issue 12, 2015.
\bibitem{Blurred Lines} Williams, Pharrel and Thicke, Robin: Blurred Lines, \textit{Star Trak Recordings}, 2013.
